Results

### 2024-04-24 Analysis/04_Summarise_results.Rmd
Update 04_Summarise_results.Rmd

## 2d
all_results_2d <- read.results("2d")

## 3d
all_results_3d <- read.results("3d")
## placeholders
all_results_4d <- read.results("3d")
all_results_5d <- read.results("3d")
all_results_8d <- read.results("3d")

## 4d
# all_results_4d <- read.results("4d")

# 5d
# all_results_5d <- read.results("5d")

## 8d
# all_results_8d <- read.results("8d")

## Empirical

## Loading empirical results
load("../Data/Processed/empirical_data-hist-extant.rda")
#empirical_data-hist-extant
empirical_hist_extant <- bkp

load("../Data/Processed/empirical_data-prehist-hist-prehist-extant.rda")
#empirical_data-prehist-hist-prehist-extant
empirical_prehist_hist_prehist_extant <- bkp

hist_table <- empirical_hist$results_table
colnames(hist_table) <- gsub("_rm1", "_rm2", colnames(hist_table))
combined_empirical <- list()
combined_empirical$results_table <- cbind(empirical_prehist$results_table, hist_table)
empirical_results <- list(empirical = combined_empirical)
```

@@

## Re-ordering results for fancyness
new_order <- c(14, 12, 3, 6,
               15, 11, 2, 8,
               7, 4, 5, 13,
               10, 9, 1)
all_results_2d <- lapply(all_results_2d, sort.metrics, order = new_order)
all_results_3d <- lapply(all_results_3d, sort.metrics, order = new_order)
empirical_results <- lapply(empirical_results, sort.metrics, order = new_order)

@@

## Fancier names
fancy_names <- c("TPD[TPD]\nregularity",
                 "hypervolume[BAT]\nregularity",
                 "dendrogram[BAT]\nregularity",
                 "dissimilarity[FD]\nregularity",
                 "TPD[TPD]\ndivergence",
                 "hypervolume[BAT]\ndivergence",
                 "dendrogram[BAT]\ndivergence",
                 "dissimilarity[melodicMPD]\ndivergence(MPD)",
                 "dissimilarity[melodicRao]\ndivergence(Rao)",
                 "dissimilarity[FD]\ndivergence(Rao)",
                 "dissimilarity[FD]\ndivergence",
                 "TPD[TPD]\nrichness",
                 "hypervolume[BAT]\nrichness",
                 "convex hull[BAT]\nrichness",
                 "dendrogram[BAT]\nrichness")
```

@@

```{r, echo = FALSE}
## Extracting all the scaled results
scaled_results_2d <- extract.table(all_results_2d, scale.method = "between")
scaled_within_2d  <- extract.table(all_results_2d, scale.method = "within")
scaled_results_3d <- extract.table(all_results_3d, scale.method = "between")
scaled_within_3d  <- extract.table(all_results_3d, scale.method = "within")
scaled_results_emp<- extract.table(empirical_results, scale.method = "between")
scaled_within_emp <- extract.table(empirical_results, scale.method = "within")
```

@@

```{r, echo = FALSE}
## Slope and R2 for each model
model_fits_2d  <- lapply(scaled_results_2d, fit.model.rm)
model_fits_3d  <- lapply(scaled_results_3d, fit.model.rm)
model_fits_emp <- lapply(scaled_results_emp, fit.model.rm)

## Differences between stressor and random
null_differences_2d  <- lapply(all_results_2d, paired.tests)
null_differences_3d  <- lapply(all_results_3d, paired.tests)
null_differences_emp <- lapply(empirical_results, paired.tests)

## Making the fancy tables
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
null_table_2d   <- fancy.table(null_differences_2d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_3d   <- fancy.table(null_differences_3d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), c(4, 6)))
```

@@

## Medians
points(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
points(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
points(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
points(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
points(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## Linkings
lines(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
lines(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
lines(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
lines(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
lines(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## 95% CI
dimensions <- c(2,3,4,5,8)
for(one_ci in 1:5) {
  lines(y = c(times_tree[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.00, col = metric_cols[1])
}
for(one_ci in 1:5) {
  lines(y = c(times_dissimilarity[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.04, col = metric_cols[2])
}
for(one_ci in 1:5) {
  lines(y = c(times_hull[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.08, col = metric_cols[3])
}
for(one_ci in 1:5) {
  lines(y = c(times_hypervolume[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.12, col = metric_cols[4])
}
for(one_ci in 1:5) {
  lines(y = c(times_probabilities[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.16, col = metric_cols[5])
}
## legend
legend("topleft", col = metric_cols, pch = 19, legend = c("tree", "dissimilarity", "convex hull", "hypervolume", "probability density"))
```

>>>>

all_results_2d <- read.results("2d")
all_results_3d <- read.results("3d")
all_results_4d <- read.results("4d")
all_results_5d <- read.results("5d")
all_results_8d <- read.results("8d")

## Empirical
load("../Data/Processed/empirical_data.rda")
empirical_results <- list("empirical" = bkp)
```

@@

## Re-ordering results for fancyness
new_order <- c(14, 12, 3, 6,
               15, 11, 2, 8,
               7, 4, #5,
               13,
               10, 9, 1)
all_results_2d <- lapply(all_results_2d, sort.metrics, order = new_order)
all_results_3d <- lapply(all_results_3d, sort.metrics, order = new_order)
all_results_4d <- lapply(all_results_4d, sort.metrics, order = new_order)
all_results_5d <- lapply(all_results_5d, sort.metrics, order = new_order)
all_results_8d <- lapply(all_results_8d, sort.metrics, order = new_order)
empirical_results <- lapply(empirical_results, sort.metrics, order = new_order)

@@

## Fancier names
fancy_names <- c("TPD[TPD]\nregularity",
                 "hypervolume[BAT]\nregularity",
                 "dendrogram[BAT]\nregularity",
                 "dissimilarity[FD]\nregularity",
                 "TPD[TPD]\ndivergence",
                 "hypervolume[BAT]\ndivergence",
                 "dendrogram[BAT]\ndivergence",
                 "dissimilarity[melodicMPD]\ndivergence(MPD)",
                 "dissimilarity[melodicRao]\ndivergence(Rao)",
                 "dissimilarity[FD]\ndivergence(Rao)",
                 #"dissimilarity[FD]\ndivergence",
                 "TPD[TPD]\nrichness",
                 "hypervolume[BAT]\nrichness",
                 "convex hull[BAT]\nrichness",
                 "dendrogram[BAT]\nrichness")
```

@@

```{r, echo = FALSE}
## Extracting all the scaled results
scaled_results_2d <- extract.table(all_results_2d, scale.method = "between")
scaled_within_2d  <- extract.table(all_results_2d, scale.method = "within")
scaled_results_3d <- extract.table(all_results_3d, scale.method = "between")
scaled_within_3d  <- extract.table(all_results_3d, scale.method = "within")
scaled_results_4d <- extract.table(all_results_4d, scale.method = "between")
scaled_within_4d  <- extract.table(all_results_4d, scale.method = "within")
scaled_results_5d <- extract.table(all_results_5d, scale.method = "between")
scaled_within_5d  <- extract.table(all_results_5d, scale.method = "within")
scaled_results_8d <- extract.table(all_results_8d, scale.method = "between")
scaled_within_8d  <- extract.table(all_results_8d, scale.method = "within")
scaled_results_emp<- extract.table(empirical_results, scale.method = "between")
scaled_within_emp <- extract.table(empirical_results, scale.method = "within")
```

@@

```{r, echo = FALSE}
## Slope and R2 for each model
model_fits_2d  <- lapply(scaled_results_2d, fit.model.rm)
model_fits_3d  <- lapply(scaled_results_3d, fit.model.rm)
model_fits_4d  <- lapply(scaled_results_4d, fit.model.rm)
model_fits_5d  <- lapply(scaled_results_5d, fit.model.rm)
model_fits_8d  <- lapply(scaled_results_8d, fit.model.rm)
model_fits_emp <- lapply(scaled_results_emp, fit.model.rm)

## Differences between stressor and random
null_differences_2d  <- lapply(all_results_2d, paired.tests)
null_differences_3d  <- lapply(all_results_3d, paired.tests)
null_differences_4d  <- lapply(all_results_4d, paired.tests)
null_differences_5d  <- lapply(all_results_5d, paired.tests)
null_differences_8d  <- lapply(all_results_8d, paired.tests)
null_differences_emp <- lapply(empirical_results, paired.tests)

## Making the fancy tables
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_4d  <- fancy.table(model_fits_4d, columns = list(c(3,4), 5))
model_table_5d  <- fancy.table(model_fits_5d, columns = list(c(3,4), 5))
model_table_8d  <- fancy.table(model_fits_8d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
null_table_2d   <- fancy.table(null_differences_2d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_3d   <- fancy.table(null_differences_3d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_4d   <- fancy.table(null_differences_4d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_5d   <- fancy.table(null_differences_5d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_8d   <- fancy.table(null_differences_8d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), c(4, 6)))
```

@@

## Medians
points(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
points(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
points(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
points(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
points(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## Linkings
lines(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
lines(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
lines(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
lines(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
lines(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## 95% CI
dimensions <- c(2,3,4,5,8)
for(one_ci in 1:5) {
  lines(y = c(times_tree[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.00, col = metric_cols[1])
}
for(one_ci in 1:5) {
  lines(y = c(times_dissimilarity[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.04, col = metric_cols[2])
}
for(one_ci in 1:5) {
  lines(y = c(times_hull[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.08, col = metric_cols[3])
}
for(one_ci in 1:5) {
  lines(y = c(times_hypervolume[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.12, col = metric_cols[4])
}
for(one_ci in 1:5) {
  lines(y = c(times_probabilities[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.16, col = metric_cols[5])
}
## legend
legend("topleft", col = metric_cols, pch = 19, legend = c("tree", "dissimilarity", "convex hull", "hypervolume", "probability density"))

## Ti me
axis(4, at = c(1, 4.1, 7, 8.189), labels = c("1 sec", "1 min", "30 min", "1 hour"), las = 2)
